Run the model

### 2019-05-04 scripts/model/1_checks.Rmd
Moved modelling scripts to Rmd files

```{r}
left_join(act, catches, by = c("year", "eez_iso3")) %>%
  drop_na() %>% 
  ggplot(mapping = aes(x = days, y = catches, fill = year)) +
  geom_smooth(method = "lm", color = "black") +
  geom_point() +
  labs(x = "Effort (days)", y = "Catches (tonnes)") +
  ggtitle("Relationship between effort and catches") +
  scale_fill_viridis_c()
```

@@

```{r}
(demands <- ggplot(data = check_E_pi, mapping = aes(x = E / 1000, y = pi, color = cty2)) +
   geom_line(size = 1) +
   geom_vline(xintercept = E / 1000, color = "red", linetype = "dashed") +
   labs(x = "E (thousand vessel-days)", y = quo(pi)) +
   guides(color = guide_legend("Patch", ncol = 2)) +
   theme(legend.position = c(1, 1),
         legend.justification = c(1, 1)) +
   scale_color_brewer(palette = "Set1")
   )
```

@@

```{r}
(demands_agg <- check_E_pi %>%
   group_by(pi) %>%
   summarise(E = sum(E)) %>%
   ggplot(aes(x = E / 1000, y = pi)) +
   geom_line() +
   geom_vline(xintercept = E / 1000, color = "red", linetype = "dashed") +
   labs(x = "E (thousand vessel-days)", y = quo(pi))
 )
```

>>>>

```{r}
(catch_effort_plot <- left_join(act, catches, by = c("year", "eez_iso3")) %>%
   drop_na() %>% 
   ggplot(mapping = aes(x = days, y = catches / 1000, fill = year)) +
   geom_smooth(method = "lm", color = "black") +
   geom_point() +
   labs(x = "Effort (days)", y = "Catches (Thousannd tonnes)") +
   ggtitle("Relationship between effort and catches") +
   scale_fill_viridis_c() +
   guides(fill = guide_colorbar(title = "Year",
                                frame.colour = "black",
                                ticks.colour = "black")))
```

```{r}
ggsave(plot = catch_effort_plot,
       filename = here("docs", "slides", "img", "catch_effort_plot.png"),
       width = 4,
       height = 3)
```

@@

```{r}
(demands <- ggplot(data = filter(check_E_pi, E < 300000),
                   mapping = aes(x = E / 1000, y = pi, color = cty2)) +
   geom_line(size = 1) +
   geom_vline(xintercept = E / 1000, color = "red", linetype = "dashed") +
   labs(x = "E (thousand vessel-days)", y = quo(pi)) +
   guides(color = guide_legend("Patch", ncol = 2)) +
   theme(legend.position = "none") +
   scale_color_brewer(palette = "Set1")
   )
```

@@

```{r}
(demands_agg <- check_E_pi %>%
   group_by(pi) %>%
   summarise(E = sum(E)) %>%
   ungroup() %>% 
   filter(E < 300000) %>% 
   ggplot(aes(x = E / 1000, y = pi)) +
   geom_line() +
   geom_vline(xintercept = E / 1000, color = "red", linetype = "dashed") +
   labs(x = "E (thousand vessel-days)", y = quo(pi))
 )
```

### 2019-05-04 scripts/model/2_run_model.Rmd
Moved modelling scripts to Rmd files

```{r}
# Load libraries
library(startR)
library(here)
library(cowplot)
library(tidyverse)

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with no reserve)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided by trading") +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

@@

## Where do vessels go?

### With no trading

```{r}
DF_results_no_trading %>% 
  filter(!Country == "HS") %>%
  mutate(Country = fct_relevel(Country, "KIR")) %>% 
  ggplot() +
  geom_line(aes(
    x = R,
    y = Vessel_Days,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab(quo("Vessel-Days")) +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                ticks.colour = "black",
                                frame.colour = "black")) +
  facet_wrap(~Country, scales = "free_y")
```

>>>>

```{r}
# Load libraries
library(startR)
library(magrittr)
library(here)
library(cowplot)
library(furrr)
library(tidyverse)

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with no reserve)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme(legend.position = "None"))
```

```{r}
ggsave(plot = costs_with_trading_plot_long_axis,
       filename = here("docs", "slides", "img", "cost_with_trading_long_axis.png"),
       width = 3,
       height = 3)
```

```{r}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with no reserve)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided by trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

@@

# Allocation rules matter

```{r}
source(here("scripts", "model", "allocate.R"))
source(here("scripts", "model", "allocate_wrap.R"))
source(here("scripts", "model", "move_in_time.R"))
source(here("scripts", "model", "move_in_time_no_trading.R"))
```

We first obtain the optimal allocation by running the model until steady state and with no reserves.

```{r}

alphas <- c(0, 0.25, 0.5, 0.75, 1)

delta <- 1 / 1.1

plan(multiprocess)

allocation <-
  expand.grid(
    R = Rvec,
    theta = c(0, 0.5, 1),
    alpha = alphas,
    trade = c(T, F)
  ) %>%
  as_tibble() %>%
  mutate(
    resutls = future_pmap(
      .l = list(
        alpha = alpha,
        R = R,
        theta = theta,
        trade = trade
      ),
      .f = allocate_wrap, 
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      E = E
    )
  ) %>%
  unnest() %>%
  filter(country == "KIR") %>%
  mutate(
    rev_dir = Ei * pi,
    deltaE = Ea - Ei,
    rev_sells = deltaE * pi,
    rev_tot = rev_dir + rev_sells,
    fct = delta ^ year,
    rev_tot_disc = rev_tot * fct
  )

best_rev <- allocate_wrap(
  alpha = 0,
  R = 0,
  theta = 1,
  trade = T,
  fvec = fvec,
  r = r,
  K = K,
  p = p,
  q = q,
  Xvec = Xvec,
  beta = beta,
  c = c,
  E = E
) %>%
  filter(country == "KIR") %>%
  mutate(
    rev_dir = Ei * pi,
    deltaE = Ea - Ei,
    rev_sells = deltaE * pi,
    rev_tot = rev_dir + rev_sells,
    fct = delta ^ year,
    rev_tot_disc = rev_tot * fct
  ) %$%
  sum(rev_tot_disc)
```

```{r}
(allocation_cost_plot <- allocation %>%
  mutate(trade = ifelse(trade, "Trading", "No Trading"),
         theta = as.character(theta)) %>% 
  group_by(trade, alpha, R, theta) %>%
  summarize(rev = sum(rev_tot_disc)) %>%
  ungroup() %>%
  mutate(cost = (best_rev - rev) / best_rev) %>%
  ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with no reserve)") +
  scale_color_viridis_c() +
  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
  ggtheme_plot() +
  facet_wrap(~trade) +
  guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")")),
         linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"))))
```

```{r}
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "slides", "img", "allocation_cost_plot.pdf"),
  width = 5,
  height = 3
)
```

```{r}
allocation %>%
  filter(!trade) %>% 
  ggplot(aes(x = year, y = Ea, color = R, group = paste(alpha, R, theta))) +
  geom_line(size = 1) +
  facet_grid(alpha ~ theta) +
  scale_color_viridis_c() +
  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
  ggtheme_plot()
```

```{r}
allocation %>%
  filter(theta == 0.5, !trade) %>% 
  ggplot(aes(x = year, y = Xi, color = R, group = paste(alpha, R))) +
  geom_line(size = 1) +
  facet_grid(~alpha) +
  scale_color_viridis_c() +
  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
  ggtheme_plot()
```
